---
title: "Exploring NHTSA's FARS data"
author: "Valter Beakovic"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## The data

The data comes in raw format (*.bz2 files) and the functions access them in the background. The files can be found in the inst/extdata folder of the package.

## Using the summary function

The package has a fars_summarize_years() function which calculates the number of accident per month for the year(s) given as argument to the function.
Two examples

```{r}
fars::fars_summarize_years(2013)
fars::fars_summarize_years(c(2013, 2014))
```


## Using the map function

The package has a fars_map_state() function that draws the the map of the selected states with loacations of the accidents.
Example

```{r}
fars::fars_map_state(1, 2013)
```

## State codes

State codes(numbers) to use with the fars_map_state() function together with addtional information can be found [here](http://www.nber.org/fars/ftp.nhtsa.dot.gov/fars/FARS-DOC/Analytical%20User%20Guide/USERGUIDE-2015.pdf)
